{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-01 Paper/main.tex
Added some crowded matrix notation.

	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression.

@@

>>>>

	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression. Define therefore the following objects

	\begin{equation}
		Y = \begin{pmatrix}
				y_1 \\ \vdots \\ y_n
			\end{pmatrix}, \quad
		Z = \begin{pmatrix}
				1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
				\vdots & \vdots & \ddots & \vdots \\
				1 & \tilde{Z}_{n,1} & \dots & \tilde{Z}_{n,J}
			\end{pmatrix}
	\end{equation}

	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$ and an estimate of the coefficient function can be derived accordingly.

	\begin{equation}
		b^L = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{L+1} \quad \hat{\alpha} = b_{1}^{L} \quad \hat{\beta}^L(t) = \sum_{j = 1}^{J} b_{j+1}^L \phi_j(t)
	\end{equation}

@@

	As in the previous section, this equation again lends itself for estimation with OLS. Define the following objects:

	\begin{equation}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
			\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{\xi}^{1,L}_{1} & \dots & \tilde{\xi}^{M,L}_{1} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{\xi}^{1,L}_{3} & \dots & \tilde{\xi}^{M,L}_{3}
			\end{pmatrix}
	\end{equation}

	We can then derive the following estimators.

	\begin{equation}
			\tilde{b}^{L,M} = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{M+1} \quad \hat{\tilde{\alpha}} = \tilde{b}_{1}^{L,M} \quad \hat{\tilde{\beta}}^{m,L} = \tilde{b}^{L,M}_{m+1}
	\end{equation}
